\chapter{Conclusion}
\label{chapter: Conclusion}
\section{Summary of Achievements}
In conclusion, there was the successful implementation files facilitating the necessary data manipulation, plotting and error analysis needed for financial analysis in Julia. Furthermore, we accomplished the addition of several simple prediction techniques to the package and compared them to previous Machine Learning based techniques. We also implemented a new prediction technique for stock prices centered around Behavioural Control Theory, which has never been done before. The performance and suitability of the Behavioural Control prediction algorithm was explored and a simple strategy to buy/sell stock using the predictions generated was devised and investigated.

\section{Future Work}
There is much room for improvement of the package as described in the previous chapter. More simple prediction methods can be added. Different problem formulations of the Behavioural Control Theory data estimation problem can be introduced and explored as well as the addition of several desirable elements such as Real-time buy/sell recommendations, integration of machine learning techniques and stock allocation recommendations. Furthermore, the Buy/Sell strategy can be improved by the addition of a moving window of statistical analysis as well as the inclusion of more complex concepts of buying and selling stock in order to make the simulation more realistic. Finally, improvement to the current implementation of the Behavioural Control Theory algorithm can be made by further in-depth investigation into the optimisation of parameters and inputs. 

